Modeling the near-wake of a vertical-axis cross-flow turbine with 2-D and 3-D RANS

### 2016-03-19 paper.tex
Make abstract past-tense

\begin{abstract}
The wake of a vertical-axis cross-flow turbine (CFT) is modeled numerically via
blade-resolved $k$--$\omega$ SST and Spalart--Allmaras RANS models in two and
three dimensions. Results for each case are compared with experimental
measurements of the turbine shaft power, overall drag, mean velocity, turbulence
kinetic energy, and momentum transport terms in the near-wake at one diameter
downstream. It is shown that 2-D simulations overpredict turbine loading and do
not resolve mean vertical momentum transport, which plays an important role in
the near-wake's momentum balance. The 3-D simulations fair better at predicting
performance, with the Spalart--Allmaras model predictions being closest to the
experiments. The SST model more accurately predicts the turbulence kinetic
energy while the Spalart--Allmaras model more closely matches the momentum
transport terms in the near-wake. These results show the potential of RANS as a
design tool and a way to ``interpolate'' experimental flow field measurements.
\end{abstract}

>>>>

\begin{abstract}
    The near-wake of a vertical-axis cross-flow turbine (CFT) was modeled
    numerically via blade-resolved $k$--$\omega$ SST and Spalart--Allmaras RANS
    models in two and three dimensions. Results for each case are compared with
    experimental measurements of the turbine shaft power, overall drag, mean
    velocity, turbulence kinetic energy, and momentum transport terms in the
    near-wake at one diameter downstream. It was shown that 2-D simulations
    overpredict turbine loading and do not resolve mean vertical momentum
    transport, which plays an important role in the near-wake's momentum
    balance. The 3-D simulations faired better at predicting performance, with
    the Spalart--Allmaras model predictions being closest to the experiments.
    The SST model more accurately predicted the turbulence kinetic energy while
    the Spalart--Allmaras model more closely matched the momentum transport
    terms in the near-wake. These results show the potential of blade-resolved
    RANS as a design tool and a way to ``interpolate'' experimental flow field
    measurements.
\end{abstract}
